\documentclass{article}
\usepackage{amsmath}
\usepackage{xcolor}

\title{Assignment 1}
\author{COMP2804 Winter 2020}

\begin{document}
\maketitle

\section{ID}

Name: Ryan Lo \\
Student ID: 101117765

\section{Non-Local Strings}

\begin{enumerate}
   \item What is the number of dec-strings of length n?
  
   by the Product Rule, the number of blocks is
   \[
      10^{n}
   \]

   \item What is the number of dec-strings $d_1,\ldots,d_n$ of length n such that $d1d2\neq00$. In other words, what is the number of dec-strings of length n that don't begin with 00?
 
   Therefore, by the Product Rule, then number of squarefree blocks is 
   \[
      (10^{2}-1) \times 10^{n-2}
   \]
   \[
      10^{n} - 10^{n-2}
   \]
  
   \item What is the number of dec-strings $d_1,\ldots,d_n$ of length n such that $d_1d_2\neq00$ and $d_2d_3\neq11$?
  
   Therefore, by the Product Rule, then number of non-local blocks is 
   \[
      10^{n} - 10^{n-2} - 10^{n-2}
   \]
   \[
      (10^3 - (2 \times 10)) \times 10^{n-3}
   \]  
   \item What is the number of dec-strings $d_1,\ldots,d_n$ of length $n$ such that $d_1d_2\neq00$ and $d_2d_3\neq01$?
   
   \[
      10^{n} - 10^{n-2} - 10^{n-2} - 1
   \]
   \[
      (10^3 - (2 \times 10) - 1) \times 10^{n-3}
   \] 

   \item What is the number of dec-strings $d_1,\ldots,d_n$ of lenght $n$ such that $d_1d_2\neq00$ or $d_1d_2d_3=111$?
 
   \[
      (10^3 - (10 + 1)) \times 10^{n-3}
   \] 
   
   \item What is the number of dec-strings $d_1,\ldots,d_n$ of length $n\geq4$ such that $d_1d_2\neq00$ or $d_3d_4\neq11$.

   \[
      (10^4 - ((4 \times 10) - 1)) \times 10^{n-4}
   \] 

   \item A dec-string $d_1,\ldots,d_n$ is $bad$ if $d_i=d_{i+1}$ or $d_i+d_{i+1}=9$ for at least one $i\in\{1,\ldots,n-1\}$ and it is good otherwise. What is the number of good dec-strings of length $n$?
   
   \item A dec-string $d_1,\ldots,d_n$ is $2-bad$ if, $d_i=d_j$ or $d_i+d_j=9$ for some $i<j \leq i+2$ and it is $2-good$ otherwise. What is the number of $2-good$ dec-strings?
   
   \item A dec-string $d_1,\ldots,d_n$ is $k-bad$ if $d_i=d_j$ or $di+dj=9$ for some $i<j \leq i+k$ and is $k-good$ otherwise. What is the number of $k-good$ dec-strings of length $n$?

\end{enumerate}

\section{Collective Arts}

Collective Arts Brewing currently makes 30 types of IPA and 6 types of Lager.

\begin{enumerate}

   \item The manager at Mike's Place needs to choose 4 types of IPA and 4 types of Lager. How many options does the manager have?

   \[
     30\times 29\times 28\times 27\times 
     6\times 5\times 4\times 3
   \]
   \[
      \binom{30}{4}\times \binom{6}{4} = 4\,637\,274\,824
   \]
   \item The 8 beers (4 IPA and 4 Lager) selected in the previous question must be placed in a line on a display shelf so that no two IPA are adjacent and no two Lager are adjacent. How many ways are there to do this?
   \[
      2 \times 4 \times 4 \times 3 \times 3 \times 2 \times 2 \times 1 \times 1 = 2 \times 4! \times 4!
   \]
   \item Continuing from the previous question, suppose that two of the beers selected were All Together Now (an IPA) and Hot Pink (a Lager). Since both cans are pink, the manager doesn't want to place them adjacent to each other. How many ways are there to do this (while still alternating between IPA and Lager)?
   
   \item How many of the arrangements from the previous question have the All Together Now among from the 4 leftmost bottles and the bottle of Hot Pink among the 4 rightmost bottles?

\end{enumerate}

\section{Restricted Permutations}

Consider all permutations of the integers 1,…,1000.

\begin{enumerate}

   \item In how many of these permutations do 1,2,3,4 appear consecutively and in this order?
   
   \item In how many of these permutations do 1,2,3,4 appear consecutively, but not necessarily in order? (For example, they may appear as 1,2,3,4, or 4,2,3,1, or 3,1,2,4, or so on.)

   \item In how many of these permutations does 1 appear before 2, 2 appear before 3, and 3 appear before 4? (In other words, 1,2,3,4 appear in order, but not necessarily consecutively.)
   
   \item In how many of these permutations do 1,2,3,4 appear in order but no two are adjacent?
   
\end{enumerate}

\section{Drug Trials}

A certain friend of mine has spent the better part of a lifetime testing recreational drugs. After thorough testing, this friend has identified 20 recreational drugs $D_1,\ldots,D_{20}$ and determined (experimentally) that any 3 of these drugs can be taken simultaneously with no adverse effects.


\begin{enumerate}

   \item Assuming my friend determined this entirely by testing, how many experiments did my friend have to perform?

   \item A new designer drug called $D_{21}$ has just hit the streets and my friend wants to know if $D_{21}$ can be added to their list. That is, can any triple of $D_1,\ldots,D_{21}$ be safely taken together? How many additional experiments does my friend need to determine this?
   
   \item Suppose my friend survives the experience and $D_{21}$ makes it onto the list. My friend takes scrupulous notes about all experiments and notices something peculiar about the answers to the preceding two questions. What combinatorial identity did my friend just discover?
   
   \item Suppose that an impatient novice wants to repeat my friends discovery using fewer experiments. This novice is willing to take 5 drugs at a time. What is the fewest number of experiments this novice can perform so that for any triple $D_i,D_j,D_k\in\{D_1,\ldots,D_{21}\}$, at least one of this novice's experiments includes $D_i$, $D_j$, and $D_k$?

\end{enumerate}

\end{document}